Laws for Creating Trust in the Blockchain Age

### 2017-09-18 tex/article.tex
small typos and better TrustChain intro

\section{Blockchain Layer (TrustChain)}
\label{sec:trustchain}
The TrustChain transaction fabric is designed around the notion of entities performing transactions with each other.\footcite{otte2017trustchain}
Each user in the TrustChain network maintains and grows their own chain of historical transactions. 
This is in contrast to traditional blockchain constructions like Bitcoin or Ethereum, where a single, global ledger is maintained, containing all transactions since the inception of the platform.
We now discuss the creation, storage and dissemination of transactions recorded on TrustChain.

@@

We have designed, implemented and evaluated a fault-tolerant, horizontally scalable consensus mechanism on top of TrustChain, capable of detecting malicious activities performed by users like double-spending\footcite{ren2017implicit}.
As far as the authors are aware, this is the first horizontally scalable blockchain fabric.
We have built our system based on three important objectives:
\begin{enumerate}
	\item Reaching global consensus on a global state: global consensus renders many types of malicious activities useless since the consistent state has consent of honest users in the network.
	\item Resistance against malicious users: our consensus mechanism should be unaffected by the presence of malicious users, with or without purpose attempting to manipulate the outcome of the global consensus. Usually, these attacks are successful when the number of malicious users reaches a specific threshold.
	\item Horizontal scalability: in this context, horizontal scalability means that as more users join the TrustChain network, the global transaction throughput increases. Note that the Bitcoin system is not horizontal scalable since the global transaction throughput is not dependent on the number of users in the network.
\end{enumerate}

@@

\subsection{Trustworthiness and Reputation}
\label{sec:reputation}
One way to quantity trustworthiness in an economic environment is by using a reputation mechanism.
Reputation systems are widely used within the gig economy but the trust is often centred to a single authority.
Fifteen years of research on generic distributed reputation systems has yielded a wide variety of proposed designs and possible solutions.\footcite{delaviz2010improving}\,\footcite{delaviz2012sybilres}\,\footcite{kamvar2003eigentrust}
Prior work by us challenges the problem of estimating reputation using network flow algorithms.
This mechanism is called BarterCast and has been verified by a real-world implementation in our file-sharing software Tribler.\footcite{meulpolder2009bartercast}
The most challenging attack on decentralized reputation systems is the Sybil attack, where a malicious user manipulates his or her standing in the network by creating multiple fake identities (sybils) and initiating interactions with them.
Our recent research addresses the Sybil attack by proposing a trust mechanism, NetFlow, that bounds the profitability of such an attack.
However, this mechanism is computationally expensive and requires significant resources when the size of the network grows.
To date, the Sybil attack remains largely unsolved and solutions that prevent manifestation of such an attack are often complex.

>>>>

\section{Blockchain Layer (TrustChain)}
\label{sec:trustchain}
The TrustChain transaction fabric is designed around the notion of entities performing transactions with each other.\footcite{otte2017trustchain}
Each user in the TrustChain network maintains and grows their own chain of historical transactions. 
This is in contrast to traditional blockchain constructions like Bitcoin or Ethereum, where a single, global ledger is maintained, containing all transactions since the inception of the platform.
%NOW, explain why the readers will be presented with lot of engineering details on
%signatures etc.
TrustChain is significantly faster than Bitcoin or Ethereum and is specifically designed to scale.\footcite{githubissueconsensus}.
TrustChain is simpler, does not have miners, relaxes the need for global replication of transactions, and removes the need for grouping transactions in blocks.
We now discuss the creation, storage and dissemination of transactions recorded on TrustChain.

@@

We have designed, implemented and evaluated a fault-tolerant, horizontally scalable consensus mechanism on top of TrustChain, capable of detecting malicious activities performed by users like double-spending\footcite{ren2017implicit}.
As far as the authors are aware, this is the first true horizontally scalable blockchain fabric.
We have built our system based on three important objectives:
\begin{enumerate}
	\item Reaching global consensus on a global state: global consensus renders many types of malicious activities useless since the consistent state has consent of honest users in the network.
	\item Resistance against malicious users: our consensus mechanism should be unaffected by the presence of malicious users, with or without purpose attempting to manipulate the outcome of the global consensus. Usually, these attacks are successful when the number of malicious users reaches a specific threshold.
	\item Horizontal scalability: in this context, horizontal scalability means that as more users join the TrustChain network, the global transaction throughput increases. Note that the Bitcoin system is not horizontal scalable since the global transaction throughput is not dependent on the number of users in the network.
\end{enumerate}

@@

\subsection{Trustworthiness and Reputation}
\label{sec:reputation}
One way to quantify trustworthiness in an economic environment is by using a reputation mechanism.
Reputation systems are widely used within the gig economy but the trust is often centered around a single authority.
Fifteen years of research on generic distributed reputation systems has yielded a wide variety of proposed designs and possible solutions.\footcite{delaviz2010improving}\,\footcite{delaviz2012sybilres}\,\footcite{kamvar2003eigentrust}
Prior work by us challenges the problem of estimating reputation using network flow algorithms.
This mechanism is called BarterCast and has been verified by a real-world implementation in our file-sharing software Tribler.\footcite{meulpolder2009bartercast}
The most challenging attack on decentralized reputation systems is the Sybil attack, where a malicious user manipulates his or her standing in the network by creating multiple fake identities (sybils) and initiating interactions with them.
Our recent research addresses the Sybil attack by proposing a trust mechanism, NetFlow, that bounds the profitability of such an attack.
However, this mechanism is computationally expensive and requires significant resources when the size of the network grows.
To date, the Sybil attack remains largely unsolved and solutions that prevent manifestation of such an attack are often complex.
